Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-09-25 paper/paper.tex

\title{Towards Accelerating checkpointed adjoint computations in full waveform
  inversion using lossy compression
}

@@

\section{Introduction}
Introduce fulll waveform inversion as an adjoint based optimization
problem

introduce revolve based checkpointing - cite revolve, pyrevolve

@@

@@

test case setup.
requirements: should be realistic, numerically stable (to get
realistic compression), big domain,
large number of timesteps
Can we use a SEAM model here?
\section{Compression algorithms}
\subsection{Lossless}
ZLib

@@

@@

at least 3 compression algorithms compared

vary compression ratio within bound established in previous section

@@

>>>>

\title{Combining checkpointing and data compression\\ for high frequency seismic imaging
}

@@

\section{Introduction}
introduce revolve based checkpointing - cite revolve, pyrevolve

@@

Briefly introduce full waveform inversion as an adjoint based optimization
problem. This can be relatively short, as this is only one of many use cases
for our technique.

@@

test case setup.
requirements: should be realistic, numerically stable (to get
realistic compression), big domain,
large number of timesteps
Can we use a SEAM model here?

\section{Compression algorithms}
\subsection{Lossless}
ZLib

@@

For this paper, we can probably focus on only zfp using 1-3 different precision settings
(nearly lossless, very lossy, something reasonable).

@@

%at least 3 compression algorithms compared

%vary compression ratio within bound established in previous section

@@

Future work:
\begin{itemize}
\item Acceptable error bounds
\item A posteriori and a priori metrics
\item Relationship between compression error and field error, propagation of errors in forward simulation
\item Relationship between compression error and gradient error in cross-correlation
\item What else?
\end{itemize}
